Effects of CHILDREN's programs

### 2020-02-25 paper.Rnw
bk

\begin{figure}
  \caption{Yearly dynamics of total grants in Meals program}
  \label{totalGrantsDyn}

<<echo=FALSE>>=
totalGrantsDyn = readRDS("./ANALYSIS/GRAPHS/PAPER/totalRealSubTrend.Rds")
print(totalGrantsDyn)
@

\floatfoot{This graph shows the development of the sum of all grants in the Meals program. We have deflated the values to 2015 euros using the price index related to food and non-alcoholic beverages(in German: Nahrungsmittel und alkoholfreie Getränke) provided by the Federal Statistical Office of Germany (Statistisches Bundesamt).}
\end{figure}

@@

stargazer(list(lm_ms, lm_ts), title = "Regression outcome: Grants", align = TRUE)  
@

@@

<<Health Regressions time plots, echo=FALSE, message=FALSE>>=
Health_timeplots <- readRDS("./ANALYSIS/GRAPHS/PAPER/Health_Year.Rds")
print(Health_timeplots)
@

>>>>

\begin{figure}
  \caption{Yearly dynamics of total grants in Meals and Trips program}
  \label{totalGrantsDyn}

<<Grant Trend, echo=FALSE, message=FALSE>>=
totalGrantsDyn = readRDS("./ANALYSIS/GRAPHS/PAPER/summaryStatistics_Subsidy.Rds")
print(totalGrantsDyn)
@

\floatfoot{This graph shows the development of grants in the Meals compared to the Trips program. We distinguish between the sum of grants in one year, the median and the median grant per beneficiary. From left to right: Meals, Trips, from top to bottom: sum, median, median per beneficiary. We have deflated the values to 2015 euros using the price index related to food and non-alcoholic beverages(in German: Nahrungsmittel und alkoholfreie Getränke) for the Meals progam and the price index related to Leisure, Entertainment and Culture (in German: Freizeit, Unterhaltung, Kultur) provided by the Federal Statistical Office of Germany (Statistisches Bundesamt).}
\end{figure}

\begin{figure}
  \caption{Health outcome over time}
  \label{Health_timeplots}
<<Health time plots, echo=FALSE, message=FALSE>>=
Health_timeplots <- readRDS("./ANALYSIS/GRAPHS/PAPER/Health_Year.Rds")
print(Health_timeplots)
@
\floatfoot{In its yearly surveys CHILDREN asks about three variables closley related to a healthy diet. These are the degree to which beneficiaries: are healthier (lessIll\_ordered), have a growing appreciation for a healthier diet (dietaryKnowledge\_ordered), and have increased their knowledge about what constitutes a healthy diet (appreciateHealthy\_ordered).
The x-axis plots the year. The y-axis displays the share of organizarions in each category of the health outcome. The possible values are: all(coded as 4), most (3), some (2), few (1), and none (coded as 0). For example, if an organization says that most beneficiaries are healthier, then this would be coded as 3.}
\end{figure}

\begin{figure}
  \caption{Equality of opportunities over time}
  \label{Equality_timeplots}
<<Equality time plots, echo=FALSE, message=FALSE>>=
Equality_timeplots <- readRDS("./ANALYSIS/GRAPHS/PAPER/Equality_Year.Rds")
print(Equality_timeplots)
@
\floatfoot{In its yearly surveys CHILDREN has always asked about two variables closley related to increasing the beneficiaries' equality of opportunities. These are the degree to which beneficiaries: have more selfworth (selfworth\_ordered) and have a growing understanding for everyday expertise (dayToDaySkills\_ordered).  
The x-axis plots the year. The y-axis displays the share of organizarions in each category of the health outcome. The possible values are: all(coded as 4), most (3), some (2), few (1), and none (coded as 0). For example, if an organization says that most beneficiaries have more selfowrth, then this would be coded as 3.}
\end{figure}

@@

texreg(list(lm_ms, lm_ts), caption = "Grants Regressions", custom.model.names = c("Number of Meals", "Number of Trips"))
@

@@

### 2020-02-25 paper.tex
bk

Regression fit output with texreg\\

\begin{table}
\begin{center}
\begin{tabular}{l c c }
\hline
 & Model 1 & Model 2 \\
\hline
(Intercept)      & $-12089.14^{*}$ & $3.70^{***}$ \\
                 & $(5192.86)$     & $(0.33)$     \\
realSubsidy      & $2.61^{***}$    &              \\
                 & $(0.57)$        &              \\
realTripsSubsidy &                 & $0.00^{*}$   \\
                 &                 & $(0.00)$     \\
\hline
R$^2$            & 0.43            & 0.05         \\
Adj. R$^2$       & 0.43            & 0.04         \\
Num. obs.        & 329             & 322          \\
RMSE             & 39992.79        & 2.96         \\
\hline
\multicolumn{3}{l}{\scriptsize{$^{***}p<0.001$, $^{**}p<0.01$, $^*p<0.05$}}
\end{tabular}
\caption{Statistical models}
\label{table:coefficients}
\end{center}
\end{table}

@@

% latex table generated in R 3.6.2 by xtable 1.8-4 package
% Tue Feb 25 17:48:03 2020
\begin{table}[ht]
\centering
\begin{tabular}{mmmmm}
  \hline
Year & Beneficiaries, Meals & Beneficiaries, Trips & Organizations, Meals & Organizations, Trips \\ 
  \hline
2011 & 3748.0 &  & 52 &  \\ 
  2012 & 3556.0 & 2803.0 & 51 & 44 \\ 
  2013 & 4015.0 & 2823.0 & 55 & 42 \\ 
  2014 & 4685.0 & 2752.0 & 55 & 43 \\ 
  2015 & 5857.0 & 3823.0 & 55 & 49 \\ 
  2016 & 3075.0 & 3819.0 & 59 & 48 \\ 
  2017 & 4895.0 & 4150.0 & 64 & 48 \\ 
  2018 & 5102.5 & 6911.0 & 68 & 49 \\ 
   \hline
\end{tabular}
\caption{Summary Statistics} 
\end{table}

@@

\begin{figure}
  \caption{Yearly dynamics of total grants in Meals program}
  \label{totalGrantsDyn}

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{verbatim}
## NULL
\end{verbatim}
\end{kframe}
\end{knitrout}

\floatfoot{This graph shows the development of the sum of all grants in the Meals program. We have deflated the values to 2015 euros using the price index related to food and non-alcoholic beverages(in German: Nahrungsmittel und alkoholfreie Getränke) provided by the Federal Statistical Office of Germany (Statistisches Bundesamt).}
\end{figure}

@@

\begin{kframe}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error: \$ operator not defined for this S4 class}}\end{kframe}

@@

{\centering \includegraphics[width=0.8\textwidth]{figure/HealthRegressionsPercentageplots-1}

@@

{\centering \includegraphics[width=0.8\textwidth]{figure/HealthRegressionsTimePlots-1}

% Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
% Date and time: Di, Feb 25, 2020 - 17:48:07
% Requires LaTeX packages: dcolumn 
\begin{table}[!htbp] \centering 
  \caption{Regression outcome: Health} 
  \label{} 
\begin{tabular}{@{\extracolsep{5pt}}lD{.}{.}{-3} D{.}{.}{-3} } 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \multicolumn{2}{c}{\textit{Dependent variable:}} \\ 
\cline{2-3} 
\\[-1.8ex] & \multicolumn{2}{c}{ } \\ 
\\[-1.8ex] & \multicolumn{1}{c}{(1)} & \multicolumn{1}{c}{(2)}\\ 
\hline \\[-1.8ex] 
 DGECriteriaNoScaled & 0.112^{*} & 0.266^{***} \\ 
  & (0.063) & (0.065) \\ 
  & & \\ 
 Constant & 0.015 & -0.026 \\ 
  & (0.067) & (0.070) \\ 
  & & \\ 
\hline \\[-1.8ex] 
\hline 
\hline \\[-1.8ex] 
\textit{Note:}  & \multicolumn{2}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
\end{tabular} 
\end{table}

% Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
% Date and time: Di, Feb 25, 2020 - 17:48:08
% Requires LaTeX packages: dcolumn 
\begin{table}[!htbp] \centering 
  \caption{Regression outcome: Chance Equality} 
  \label{} 
\begin{tabular}{@{\extracolsep{5pt}}lD{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} } 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \multicolumn{4}{c}{\textit{Dependent variable:}} \\ 
\cline{2-5} 
\\[-1.8ex] & \multicolumn{4}{c}{ } \\ 
\\[-1.8ex] & \multicolumn{1}{c}{(1)} & \multicolumn{1}{c}{(2)} & \multicolumn{1}{c}{(3)} & \multicolumn{1}{c}{(4)}\\ 
\hline \\[-1.8ex] 
 realSubsidy & 0.003^{***} & 0.003^{***} & 0.00000 & 0.00001^{***} \\ 
  & (0.001) & (0.001) & (0.00000) & (0.00000) \\ 
  & & & & \\ 
 Constant & -13.419^{**} & -13.481^{**} & -0.056 & -0.158^{***} \\ 
  & (5.715) & (5.727) & (0.063) & (0.060) \\ 
  & & & & \\ 
\hline \\[-1.8ex] 
\hline 
\hline \\[-1.8ex] 
\textit{Note:}  & \multicolumn{4}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
\end{tabular} 
\end{table}

@@

% Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
% Date and time: Di, Feb 25, 2020 - 17:48:08
% Requires LaTeX packages: dcolumn rotating 
\begin{sidewaystable}[!htbp] \centering 
  \caption{Regression Results} 
  \label{} 
\begin{tabular}{@{\extracolsep{5pt}}lD{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} } 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \multicolumn{4}{c}{\textit{Dependent variable:}} \\ 
\cline{2-5} 
\\[-1.8ex] & \multicolumn{4}{c}{selfworth} \\ 
\\[-1.8ex] & \multicolumn{1}{c}{(1)} & \multicolumn{1}{c}{(2)} & \multicolumn{1}{c}{(3)} & \multicolumn{1}{c}{(4)}\\ 
\hline \\[-1.8ex] 
 Constant & 2.796^{***} & 2.870^{***} & 2.774^{***} & 2.847^{***} \\ 
  & (0.065) & (0.095) & (0.092) & (0.107) \\ 
  & & & & \\ 
 treatEF & 0.249^{***} & 0.320^{***} & 0.253^{***} & 0.333^{***} \\ 
  & (0.074) & (0.097) & (0.075) & (0.100) \\ 
  & & & & \\ 
\hline \\[-1.8ex] 
ID fixed effects & No & No & Yes & Yes \\ 
Time fixed effects & No & Yes & No & Yes \\ 
Observations & \multicolumn{1}{c}{430} & \multicolumn{1}{c}{430} & \multicolumn{1}{c}{430} & \multicolumn{1}{c}{430} \\ 
R$^{2}$ & \multicolumn{1}{c}{0.026} & \multicolumn{1}{c}{0.035} & \multicolumn{1}{c}{0.026} & \multicolumn{1}{c}{0.036} \\ 
Adjusted R$^{2}$ & \multicolumn{1}{c}{0.024} & \multicolumn{1}{c}{0.017} & \multicolumn{1}{c}{0.022} & \multicolumn{1}{c}{0.015} \\ 
Residual Std. Error & \multicolumn{1}{c}{0.642 (df = 428)} & \multicolumn{1}{c}{0.644 (df = 421)} & \multicolumn{1}{c}{0.642 (df = 427)} & \multicolumn{1}{c}{0.645 (df = 420)} \\ 
F Statistic & \multicolumn{1}{c}{11.417$^{***}$ (df = 1; 428)} & \multicolumn{1}{c}{1.916$^{*}$ (df = 8; 421)} & \multicolumn{1}{c}{5.752$^{***}$ (df = 2; 427)} & \multicolumn{1}{c}{1.724$^{*}$ (df = 9; 420)} \\ 
\hline 
\hline \\[-1.8ex] 
\textit{Note:}  & \multicolumn{4}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
\end{tabular} 
\end{sidewaystable}

@@

% latex table generated in R 3.6.2 by xtable 1.8-4 package
% Tue Feb 25 17:48:08 2020
\begin{table}[ht]
\centering
\begin{tabular}{rllr}
  \hline
 & Variable, Meals & Mapping, Meals & Information, Meals \\ 
  \hline
1 & participateMore & participateMore & 1.00 \\ 
  2 & tasksLunch & tasksLunch & 1.00 \\ 
  3 & ownIdeas & ownIdeas & 1.00 \\ 
  4 & stayLonger & stayLonger & 1.00 \\ 
  5 & dietaryKnowledge & dietaryKnowledge & 1.00 \\ 
  6 & appreciateHealthy & appreciateHealthy & 1.00 \\ 
  7 & foodCulture & foodCulture & 1.00 \\ 
  8 & lessIll & lessIll & 1.00 \\ 
  9 & betterTeamwork & betterTeamwork & 1.00 \\ 
  10 & moreRegularSchoolVisits & moreRegularSchoolVisits & 1.00 \\ 
  11 & addressProblems & addressProblems & 1.00 \\ 
  12 & reduced\_var\_1 & moreConcentrated & 0.66 \\ 
  13 & reduced\_var\_1 & moreBalanced & 0.66 \\ 
  14 & reduced\_var\_2 & monthlyCooks & 0.42 \\ 
  15 & reduced\_var\_2 & weeklyCooks & 0.42 \\ 
  16 & reduced\_var\_2 & shoppers & 0.42 \\ 
  17 & reduced\_var\_2 & easyDishes & 0.42 \\ 
  18 & reduced\_var\_3 & dayToDaySkills & 0.43 \\ 
  19 & reduced\_var\_3 & moreIndependent & 0.43 \\ 
  20 & reduced\_var\_3 & selfworth & 0.43 \\ 
  21 & reduced\_var\_3 & moreOpen & 0.43 \\ 
  22 & reduced\_var\_3 & moreConfidence & 0.43 \\ 
  23 & reduced\_var\_3 & proud & 0.43 \\ 
  24 & reduced\_var\_4 & betterReading & 0.53 \\ 
  25 & reduced\_var\_4 & betterNumbers & 0.53 \\ 
  26 & reduced\_var\_4 & betterGrades & 0.53 \\ 
  27 & reduced\_var\_5 & influenceHome & 0.41 \\ 
  28 & reduced\_var\_5 & cookAtHome & 0.41 \\ 
  29 & reduced\_var\_5 & askRecipes & 0.41 \\ 
   \hline
\end{tabular}
\caption{Partition of outcomes, Meals} 
\end{table}
% latex table generated in R 3.6.2 by xtable 1.8-4 package
% Tue Feb 25 17:48:08 2020
\begin{table}[ht]
\centering
\begin{tabular}{rllr}
  \hline
 & Variable, Trips & Mapping, Trips & Information, Trips \\ 
  \hline
1 & tripsSuggestions & tripsSuggestions & 1.00 \\ 
  2 & tripsDecisions & tripsDecisions & 1.00 \\ 
  3 & tripsOrganization & tripsOrganization & 1.00 \\ 
  4 & tripsCostCalculation & tripsCostCalculation & 1.00 \\ 
  5 & tripsBudget & tripsBudget & 1.00 \\ 
  6 & tripsMoney & tripsMoney & 1.00 \\ 
  7 & tripsReview & tripsReview & 1.00 \\ 
  8 & tripsPublicTransport & tripsPublicTransport & 1.00 \\ 
  9 & tripsMobility & tripsMobility & 1.00 \\ 
  10 & tripsAdditionalActivities & tripsAdditionalActivities & 1.00 \\ 
  11 & tripsSelfworth & tripsSelfworth & 1.00 \\ 
  12 & tripsFrustrationTolerance & tripsFrustrationTolerance & 1.00 \\ 
  13 & reduced\_var\_1 & tripsSuccess & 0.68 \\ 
  14 & reduced\_var\_1 & tripsSelfEfficacy & 0.68 \\ 
  15 & reduced\_var\_2 & tripsNewPlaces & 0.60 \\ 
  16 & reduced\_var\_2 & tripsNewCommunities & 0.60 \\ 
  17 & reduced\_var\_2 & tripsNewIdeas & 0.60 \\ 
  18 & reduced\_var\_2 & tripsSocialSkills & 0.60 \\ 
  19 & reduced\_var\_3 & tripsSpecificSkills & 0.46 \\ 
  20 & reduced\_var\_3 & tripsDayToDaySkills & 0.46 \\ 
   \hline
\end{tabular}
\caption{Partition of outcomes, Trips} 
\end{table}
\begin{kframe}

>>>>

Regression fit ouput with texreg

@@

% latex table generated in R 3.6.2 by xtable 1.8-4 package
% Tue Feb 25 18:51:50 2020
\begin{table}[ht]
\centering
\begin{tabular}{mmmmm}
  \hline
Year & Beneficiaries, Meals & Beneficiaries, Trips & Organizations, Meals & Organizations, Trips \\ 
  \hline
2011 & 3748.0 &  & 52 &  \\ 
  2012 & 3556.0 & 2803.0 & 51 & 44 \\ 
  2013 & 4015.0 & 2823.0 & 55 & 42 \\ 
  2014 & 4685.0 & 2752.0 & 55 & 43 \\ 
  2015 & 5857.0 & 3823.0 & 55 & 49 \\ 
  2016 & 3075.0 & 3819.0 & 59 & 48 \\ 
  2017 & 4895.0 & 4150.0 & 64 & 48 \\ 
  2018 & 5102.5 & 6911.0 & 68 & 49 \\ 
   \hline
\end{tabular}
\caption{Summary Statistics} 
\end{table}

@@

\begin{figure}
  \caption{Yearly dynamics of total grants in Meals and Trips program}
  \label{totalGrantsDyn}

{\centering \includegraphics[width=0.8\textwidth]{figure/Grant_Trend-1}

\floatfoot{This graph shows the development of grants in the Meals compared to the Trips program. We distinguish between the sum of grants in one year, the median and the median grant per beneficiary. From left to right: Meals, Trips, from top to bottom: sum, median, median per beneficiary. We have deflated the values to 2015 euros using the price index related to food and non-alcoholic beverages(in German: Nahrungsmittel und alkoholfreie Getränke) for the Meals progam and the price index related to Leisure, Entertainment and Culture (in German: Freizeit, Unterhaltung, Kultur) provided by the Federal Statistical Office of Germany (Statistisches Bundesamt).}
\end{figure}

\begin{figure}
  \caption{Health outcome over time}
  \label{Health_timeplots}
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}

{\centering \includegraphics[width=0.8\textwidth]{figure/Health_time_plots-1}

\end{knitrout}
\floatfoot{In its yearly surveys CHILDREN asks about three variables closley related to a healthy diet. These are the degree to which beneficiaries: are healthier (lessIll\_ordered), have a growing appreciation for a healthier diet (dietaryKnowledge\_ordered), and have increased their knowledge about what constitutes a healthy diet (appreciateHealthy\_ordered).
The x-axis plots the year. The y-axis displays the share of organizarions in each category of the health outcome. The possible values are: all(coded as 4), most (3), some (2), few (1), and none (coded as 0). For example, if an organization says that most beneficiaries are healthier, then this would be coded as 3.}
\end{figure}

\begin{figure}
  \caption{Equality of opportunities over time}
  \label{Equality_timeplots}
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}

{\centering \includegraphics[width=0.8\textwidth]{figure/Equality_time_plots-1}

\end{knitrout}
\floatfoot{In its yearly surveys CHILDREN has always asked about two variables closley related to increasing the beneficiaries' equality of opportunities. These are the degree to which beneficiaries: have more selfworth (selfworth\_ordered) and have a growing understanding for everyday expertise (dayToDaySkills\_ordered).  
The x-axis plots the year. The y-axis displays the share of organizarions in each category of the health outcome. The possible values are: all(coded as 4), most (3), some (2), few (1), and none (coded as 0). For example, if an organization says that most beneficiaries have more selfowrth, then this would be coded as 3.}
\end{figure}

@@

\begin{table}
\begin{center}
\begin{tabular}{l c c }
\hline
 & Number of Meals & Number of Trips \\
\hline
(Intercept)      & $-12089.14^{*}$ & $3.70^{***}$ \\
                 & $(5192.86)$     & $(0.33)$     \\
realSubsidy      & $2.61^{***}$    &              \\
                 & $(0.57)$        &              \\
realTripsSubsidy &                 & $0.00^{*}$   \\
                 &                 & $(0.00)$     \\
\hline
R$^2$            & 0.43            & 0.05         \\
Adj. R$^2$       & 0.43            & 0.04         \\
Num. obs.        & 329             & 322          \\
RMSE             & 39992.79        & 2.96         \\
\hline
\multicolumn{3}{l}{\scriptsize{$^{***}p<0.001$, $^{**}p<0.01$, $^*p<0.05$}}
\end{tabular}
\caption{Grants Regressions}
\label{table:coefficients}
\end{center}
\end{table}

@@

{\centering \includegraphics[width=0.8\textwidth]{figure/Health_Regressions_percentageplots-1}

@@

% Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
% Date and time: Di, Feb 25, 2020 - 18:51:55
% Requires LaTeX packages: dcolumn 
\begin{table}[!htbp] \centering 
  \caption{Regression outcome: Health} 
  \label{} 
\begin{tabular}{@{\extracolsep{5pt}}lD{.}{.}{-3} D{.}{.}{-3} } 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \multicolumn{2}{c}{\textit{Dependent variable:}} \\ 
\cline{2-3} 
\\[-1.8ex] & \multicolumn{2}{c}{ } \\ 
\\[-1.8ex] & \multicolumn{1}{c}{(1)} & \multicolumn{1}{c}{(2)}\\ 
\hline \\[-1.8ex] 
 DGECriteriaNoScaled & 0.112^{*} & 0.266^{***} \\ 
  & (0.063) & (0.065) \\ 
  & & \\ 
 Constant & 0.015 & -0.026 \\ 
  & (0.067) & (0.070) \\ 
  & & \\ 
\hline \\[-1.8ex] 
\hline 
\hline \\[-1.8ex] 
\textit{Note:}  & \multicolumn{2}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
\end{tabular} 
\end{table}

% Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
% Date and time: Di, Feb 25, 2020 - 18:51:55
% Requires LaTeX packages: dcolumn 
\begin{table}[!htbp] \centering 
  \caption{Regression outcome: Chance Equality} 
  \label{} 
\begin{tabular}{@{\extracolsep{5pt}}lD{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} } 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \multicolumn{4}{c}{\textit{Dependent variable:}} \\ 
\cline{2-5} 
\\[-1.8ex] & \multicolumn{4}{c}{ } \\ 
\\[-1.8ex] & \multicolumn{1}{c}{(1)} & \multicolumn{1}{c}{(2)} & \multicolumn{1}{c}{(3)} & \multicolumn{1}{c}{(4)}\\ 
\hline \\[-1.8ex] 
 realSubsidy & 0.003^{***} & 0.003^{***} & 0.00000 & 0.00001^{***} \\ 
  & (0.001) & (0.001) & (0.00000) & (0.00000) \\ 
  & & & & \\ 
 Constant & -13.419^{**} & -13.481^{**} & -0.056 & -0.158^{***} \\ 
  & (5.715) & (5.727) & (0.063) & (0.060) \\ 
  & & & & \\ 
\hline \\[-1.8ex] 
\hline 
\hline \\[-1.8ex] 
\textit{Note:}  & \multicolumn{4}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
\end{tabular} 
\end{table}

@@

% Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
% Date and time: Di, Feb 25, 2020 - 18:51:55
% Requires LaTeX packages: dcolumn rotating 
\begin{sidewaystable}[!htbp] \centering 
  \caption{Regression Results} 
  \label{} 
\begin{tabular}{@{\extracolsep{5pt}}lD{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} } 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \multicolumn{4}{c}{\textit{Dependent variable:}} \\ 
\cline{2-5} 
\\[-1.8ex] & \multicolumn{4}{c}{selfworth} \\ 
\\[-1.8ex] & \multicolumn{1}{c}{(1)} & \multicolumn{1}{c}{(2)} & \multicolumn{1}{c}{(3)} & \multicolumn{1}{c}{(4)}\\ 
\hline \\[-1.8ex] 
 Constant & 2.796^{***} & 2.870^{***} & 2.774^{***} & 2.847^{***} \\ 
  & (0.065) & (0.095) & (0.092) & (0.107) \\ 
  & & & & \\ 
 treatEF & 0.249^{***} & 0.320^{***} & 0.253^{***} & 0.333^{***} \\ 
  & (0.074) & (0.097) & (0.075) & (0.100) \\ 
  & & & & \\ 
\hline \\[-1.8ex] 
ID fixed effects & No & No & Yes & Yes \\ 
Time fixed effects & No & Yes & No & Yes \\ 
Observations & \multicolumn{1}{c}{430} & \multicolumn{1}{c}{430} & \multicolumn{1}{c}{430} & \multicolumn{1}{c}{430} \\ 
R$^{2}$ & \multicolumn{1}{c}{0.026} & \multicolumn{1}{c}{0.035} & \multicolumn{1}{c}{0.026} & \multicolumn{1}{c}{0.036} \\ 
Adjusted R$^{2}$ & \multicolumn{1}{c}{0.024} & \multicolumn{1}{c}{0.017} & \multicolumn{1}{c}{0.022} & \multicolumn{1}{c}{0.015} \\ 
Residual Std. Error & \multicolumn{1}{c}{0.642 (df = 428)} & \multicolumn{1}{c}{0.644 (df = 421)} & \multicolumn{1}{c}{0.642 (df = 427)} & \multicolumn{1}{c}{0.645 (df = 420)} \\ 
F Statistic & \multicolumn{1}{c}{11.417$^{***}$ (df = 1; 428)} & \multicolumn{1}{c}{1.916$^{*}$ (df = 8; 421)} & \multicolumn{1}{c}{5.752$^{***}$ (df = 2; 427)} & \multicolumn{1}{c}{1.724$^{*}$ (df = 9; 420)} \\ 
\hline 
\hline \\[-1.8ex] 
\textit{Note:}  & \multicolumn{4}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
\end{tabular} 
\end{sidewaystable}

@@

% latex table generated in R 3.6.2 by xtable 1.8-4 package
% Tue Feb 25 18:51:55 2020
\begin{table}[ht]
\centering
\begin{tabular}{rllr}
  \hline
 & Variable, Meals & Mapping, Meals & Information, Meals \\ 
  \hline
1 & participateMore & participateMore & 1.00 \\ 
  2 & tasksLunch & tasksLunch & 1.00 \\ 
  3 & ownIdeas & ownIdeas & 1.00 \\ 
  4 & stayLonger & stayLonger & 1.00 \\ 
  5 & dietaryKnowledge & dietaryKnowledge & 1.00 \\ 
  6 & appreciateHealthy & appreciateHealthy & 1.00 \\ 
  7 & foodCulture & foodCulture & 1.00 \\ 
  8 & lessIll & lessIll & 1.00 \\ 
  9 & betterTeamwork & betterTeamwork & 1.00 \\ 
  10 & moreRegularSchoolVisits & moreRegularSchoolVisits & 1.00 \\ 
  11 & addressProblems & addressProblems & 1.00 \\ 
  12 & reduced\_var\_1 & moreConcentrated & 0.66 \\ 
  13 & reduced\_var\_1 & moreBalanced & 0.66 \\ 
  14 & reduced\_var\_2 & monthlyCooks & 0.42 \\ 
  15 & reduced\_var\_2 & weeklyCooks & 0.42 \\ 
  16 & reduced\_var\_2 & shoppers & 0.42 \\ 
  17 & reduced\_var\_2 & easyDishes & 0.42 \\ 
  18 & reduced\_var\_3 & dayToDaySkills & 0.43 \\ 
  19 & reduced\_var\_3 & moreIndependent & 0.43 \\ 
  20 & reduced\_var\_3 & selfworth & 0.43 \\ 
  21 & reduced\_var\_3 & moreOpen & 0.43 \\ 
  22 & reduced\_var\_3 & moreConfidence & 0.43 \\ 
  23 & reduced\_var\_3 & proud & 0.43 \\ 
  24 & reduced\_var\_4 & betterReading & 0.53 \\ 
  25 & reduced\_var\_4 & betterNumbers & 0.53 \\ 
  26 & reduced\_var\_4 & betterGrades & 0.53 \\ 
  27 & reduced\_var\_5 & influenceHome & 0.41 \\ 
  28 & reduced\_var\_5 & cookAtHome & 0.41 \\ 
  29 & reduced\_var\_5 & askRecipes & 0.41 \\ 
   \hline
\end{tabular}
\caption{Partition of outcomes, Meals} 
\end{table}
% latex table generated in R 3.6.2 by xtable 1.8-4 package
% Tue Feb 25 18:51:55 2020
\begin{table}[ht]
\centering
\begin{tabular}{rllr}
  \hline
 & Variable, Trips & Mapping, Trips & Information, Trips \\ 
  \hline
1 & tripsSuggestions & tripsSuggestions & 1.00 \\ 
  2 & tripsDecisions & tripsDecisions & 1.00 \\ 
  3 & tripsOrganization & tripsOrganization & 1.00 \\ 
  4 & tripsCostCalculation & tripsCostCalculation & 1.00 \\ 
  5 & tripsBudget & tripsBudget & 1.00 \\ 
  6 & tripsMoney & tripsMoney & 1.00 \\ 
  7 & tripsReview & tripsReview & 1.00 \\ 
  8 & tripsPublicTransport & tripsPublicTransport & 1.00 \\ 
  9 & tripsMobility & tripsMobility & 1.00 \\ 
  10 & tripsAdditionalActivities & tripsAdditionalActivities & 1.00 \\ 
  11 & tripsSelfworth & tripsSelfworth & 1.00 \\ 
  12 & tripsFrustrationTolerance & tripsFrustrationTolerance & 1.00 \\ 
  13 & reduced\_var\_1 & tripsSuccess & 0.68 \\ 
  14 & reduced\_var\_1 & tripsSelfEfficacy & 0.68 \\ 
  15 & reduced\_var\_2 & tripsNewPlaces & 0.60 \\ 
  16 & reduced\_var\_2 & tripsNewCommunities & 0.60 \\ 
  17 & reduced\_var\_2 & tripsNewIdeas & 0.60 \\ 
  18 & reduced\_var\_2 & tripsSocialSkills & 0.60 \\ 
  19 & reduced\_var\_3 & tripsSpecificSkills & 0.46 \\ 
  20 & reduced\_var\_3 & tripsDayToDaySkills & 0.46 \\ 
   \hline
\end{tabular}
\caption{Partition of outcomes, Trips} 
\end{table}
\begin{kframe}
